\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
insert comma
show TYPES of overlaps, not just overlaps

%%%%%%%%%%%%%%%%% Adding properties to volumes
Geometry needs to be augmented with other information for a complete MCRT simulation. Often other attributes need to be 
assigned to regions of space for example material definition, magnetic field or optical properties. These physical properties 
can be used to define the visualisation attributes of a volume.

\subsection{Overlap detection}
All MCRT codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by 
performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows the potential 
overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters 
share a face. If the resulting intersection is non-null then the overlaps can be displayed side-by-side in the visualisation. 
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
\label{fig:overlap}
\end{center}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%% Adding properties to volumes
Geometry needs to be augmented with other information for a complete MCRT simulation. Often other attributes need to be 
assigned to regions of space, for example material definition, magnetic field or optical properties. These physical properties 
can be used to define the visualisation attributes of a volume.

\subsection{Overlap detection}
All MCRT codes cannot handle spatial overlap between two geometric objects and will have ill-defined behaviour when tracking particles  
in such a situation.  A key feature of \PYGEOMETRY{} is the detection of potential overlaps in a way which is most useful to the user, it does this by 
performing an intersection operation between solid instances and determining if the resultant mesh is empty. Figure~\ref{fig:overlap} shows three different types of possible
overlaps, (a) protrusion of a daughter from the mother, (b)  finite volume intersection between two daughters  and (c) an overlap where two daughters 
share a face. If the resulting intersection is non-null then the overlaps can be displayed side-by-side in the visualisation. 
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=8cm]{./diagrams/overlap.pdf}
\caption{Schematic of the three different types of overlap between daughters of a mother logical volume.}
\label{fig:overlap}
\end{center}
\end{figure}
